% resume.tex

\documentclass[10pt,letterpaper]{article}
\usepackage[letterpaper,margin=0.75in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{mdwlist}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage{tgpagella}
\pagestyle{empty}
\setlength{\tabcolsep}{0em}

% indentsection style, used for sections that aren't already in lists
% that need indentation to the level of all text in the document
\newenvironment{indentsection}[1]%
{\begin{list}{}%
    {\setlength{\leftmargin}{#1}}%
    \item[]%
}
{\end{list}}

% opposite of above; bump a section back toward the left margin
\newenvironment{unindentsection}[1]%
{\begin{list}{}%
    {\setlength{\leftmargin}{-0.5#1}}%
    \item[]%
}
{\end{list}}

% format two pieces of text, one left aligned and one right aligned
\newcommand{\headerrow}[2]
{\begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}
    #1 &
    #2 \\
\end{tabular*}}

% make "C++" look pretty when used in text by touching up the plus signs
\newcommand{\CPP}
{C\nolinebreak[4]\hspace{-.05em}\raisebox{.22ex}{\footnotesize\bf ++}}

% and the actual content starts here
\begin{document}

\begin{center}
{\LARGE \textbf{Atanas Abrashev}}

Flat 20, Wilbraham Court,
16-18 Wilbraham Road,
Manchester, United Kingdom,
M14 6JY
\\
(+44) 7450-328-494\ \ \textbullet
\ \ atanas.abrashev@gmail.com
\end{center}

\hrule
\vspace{-0.4em}
\subsection*{Education}

\begin{itemize}
    \parskip=0.1em

    \item
    \headerrow
        {\textbf{The University of Manchester}}
        {\textbf{Manchester, United Kingdom}}
    \\
    \headerrow
        {\emph{B.Sc. Computer Science}}
        {\emph{September 2011 - June 2015}}
    \begin{itemize*}
        \item Result: First-class honours
    \end{itemize*}
\end{itemize}

\hrule
\vspace{-0.4em}
\subsection*{Work Experience}

\begin{itemize}
    \parskip=0.1em

    \item
    \headerrow
        {\textbf{Radius Payment Solutions}}
        {\textbf{Crewe, United Kingdom}}
    \\
    \headerrow
        {\emph{R\&D Engineer (Full-time)}}
        {\emph{June 2017 - Now}}
    \begin{itemize*}
        \item Data analytics using Apache Spark.
        \item Prototyping a chatbot and new algorithms for assessing driver performance.
    \end{itemize*}
    \headerrow
        {\emph{Software Developer (Full-time)}}
        {\emph{June 2015 - June 2017}}
    \begin{itemize*}
        \item Full stack web development using Django/PostgreSQL backend and React/Redux frontend.
        \item Worked to develop various applications for tracking fuel card and vehicle usage.
        \item Used Java and Spring for developing and maintaining a real-time telematics system for managing data coming from thousands of devices.
    \end{itemize*}

    \item
    \headerrow
        {\textbf{DataCentred}}
        {\textbf{Manchester, United Kingdom}}
    \\
    \headerrow
        {\emph{Cloud Platform Intern (Summer Internship)}}
        {\emph{June 2014 - September 2014}}
    \begin{itemize*}
        \item Supporting, developing and maintaining a Cloud platform based around Openstack.
        \item Used Puppet, Ruby and Python to automate the deployment of various services such as hard drive health monitoring and IPMI configuration
        \item Used Clojure and Riemann to write a filtering tool for log messages generated by Logstash and syslog.
    \end{itemize*}

    \item
    \headerrow
        {\textbf{IBM}}
        {\textbf{Hursley, United Kingdom}}
    \\
    \headerrow
        {\emph{Software Developer (Industrial Placement)}}
        {\emph{June 2013 - June 2014}}
    \begin{itemize*}
        \item Working in a very agile environment with daily scrums and planning meetings, I was placed in various positions to work on different projects of varying size.
        \item Had a chance to practice my skills in various technologies, while learning Perl and maintaining a large amount of internal APIs and tools, written in different programming languages.
        \item Gained a lot of knowledge in Unix-like operating systems, as well as how to create a stable automated environment for building and testing new software.
        \item Wrote an automation tool in Perl and Java which was based around IBM Security Appscan. My tool was used as part of the continious delivery stack in order to scan Java source code of various IBM products for vulnerabilities.
    \end{itemize*}

    \item
    \headerrow
        {\textbf{The University of Manchester}}
        {\textbf{Manchester, United Kingdom}}
    \\
    \headerrow
        {\emph{PASS Leader}}
        {\emph{September 2012 - May 2013}}
    \begin{itemize*}
        \item Received training on how to facilitate and tutor people in their studies.
        \item Conducted weekly tutorial sessions with a group of first-year Computer Science students.
        \item Prepared tutorials and ways to engage students in learning, while solidifying what I already knew.
    \end{itemize*}

    \item
    \headerrow
        {\textbf{Dunapack-Rodina AD}}
        {\textbf{Plovdiv, Bulgaria}}
    \\
    \headerrow
        {\emph{Programmer, IT Support \& Technical Translation}}
        {\emph{July 2010 - August 2011}}
    \begin{itemize*}
        \item Created front-end applications for visualizing production data output in XML format.
        \item Created statistical tools that show product output and employee effectiveness, after taking an initiative and being given permission by my supervisor.
        \item Collaborated with all levels of hierarchy within the company to translate technical documents related to the production of corrugated paper. These documents are now used actively for training new employees and I am sometimes contacted to extend on them.
    \end{itemize*}

\end{itemize}


\hrule
\vspace{-0.4em}
\subsection*{Larger Projects}

\begin{itemize}
    \parskip=0.1em

    \item
    \headerrow
        {\textbf{Gesture-Controlling an IoT Robot}}
        {\textbf{University Project}}
    \begin{itemize*}
        \item Created a robotic platform, based around the Dagu Wild Thumper Chassis
        \item Used a Raspberry Pi to talk to a T'rex Robot Controller using the Standard Firmata protocol in order to control actuators and sensors from the Pi.
        \item Created an API for controlling the robot from a web interface and built an example application that uses the Leap Motion Controller and it's API to control the robot from the Internet using hand gestures.

    \end{itemize*}

    \item
    \headerrow
        {\textbf{Particle System Simulator}}
        {\textbf{University Project}}
    \begin{itemize*}
        \item Created a particle system simulator using C and OpenGL.
        \item Provided ability to modify the engine parameters in such a way, that the same engine can render different particle effects such as rain, fire and fireworks.
    \end{itemize*}

    \item
    \headerrow
        {\textbf{SOS - Simple Operating System}}
        {\textbf{University Project}}
    \begin{itemize*}
        \item Wrote a simple operating system for the ARM processor in Assembly.
        \item It can perform process scheduling, system call dispatching and primitive memory handling.
        \item I wrote a calculator program for it, applying shunting yard algorithm to deal with complex expressions.
        \item Also wrote drivers for things like a keypad and a display to control the OS and user programs.
    \end{itemize*}

    \item
    \headerrow
        {\textbf{IBMS}}
        {\textbf{IBM Thinkpad Challenge Team Project}}
    \begin{itemize*}
        \item Team project to write a system to deal with bus scheduling and driver rostering in Java
        \item Went through the full software lifecycle, applying agile methodologies for the duration of the project.
        \item Developed a genetic algorithm with combination of other techniques to provide efficient driver rostering.
        \item Created an interface to the provided databases that was used by the team.
    \end{itemize*}

    \item
    \headerrow
        {\textbf{TGN - The Gaming Network}}
        {\textbf{University Team Project}}
    \begin{itemize*}
        \item Wrote a simplistic PHP framework for the team to use for the duration of the project.
        \item Learned about AJAX and jQuery to allow for dynamic content update.
    \end{itemize*}

    \item
    \headerrow
        {\textbf{Arduino Snake Game}}
        {\textbf{Individual Project}}
    \begin{itemize*}
        \item Created a 10x10 LED matrix.
        \item Developed an algorithm to make the Arduino microcontroller play the snake game and play music.
    \end{itemize*}

\end{itemize}

\hrule
\vspace{-0.4em}
\subsection*{Core Technical Skills}

\begin{indentsection}{\parindent}
\hyphenpenalty=1000
\begin{description*}
    \item[Languages:]
    C, Python, Java, Javascript, Perl, Puppet, SQL, Assembly, Matlab, shell scripting, Clojure, Ruby, \LaTeX
    \item[Databases/Servers:]
    PostgreSQL, Cassandra, DB2, MySQL, Oracle
    \item[IDEs/Version Control:]
    Eclipse, Visual Studio, Rational Team Concert, Git, Mercurial
    \item[Operating Systems:]
    Linux, Windows, AIX, Solaris, HP-UX, z/OS
    \item[Technologies/APIs:] React/Redux/Apollo, Django, Apache Spark, Spring, WebSocket

\end{description*}
\end{indentsection}

\hrule
\vspace{-0.4em}
\subsection*{Activities \& Interests}

\begin{itemize}
    \parskip=0.1em

    \item I greatly enjoy solving algorithmic problems and logical puzzles.
    \item Completed online courses on Algorithms, Machine Learning and Artificial Intelligence on Coursera and Udemy.
    \item Currently working on Self-Driving Card and Artificial Intelligence Nanodegrees on Udacity.
    \item Interested in electronics and microcontrollers - Arduino in particular.
    \item Previous member of my country's national logic puzzles team.
    \item Participation in online competitions, such as those offered by USACO or the IBM Mainframe Challenge.
    \item Participation in hackathons organized around university campus.

\end{itemize}

\hrule
\vspace{-0.4em}
\subsection*{Awards \& Honours}

\begin{itemize}
    \parskip=0.1em
    \item
    \headerrow
        {\textbf{Eminence \& Excellence Award}}
        {\textbf{IBM, 2014}}
    \begin{itemize*}
        \item Awarded for outstanding contribution during IT Placement Year at IBM
    \end{itemize*}

\end{itemize}
\end{document}
